Copy number inference with InferCNV

### 2024-05-23 analyses/cell-type-ewings/template_notebooks/03-copykat.Rmd

# check if marker gene annotations are present 
if(all(is.na(manual_classifications_df$marker_gene_classification))){
  has_marker_gene <- FALSE
} else {
  has_marker_gene <- TRUE 
}

>>>>

# check if marker gene annotations are present 
if(all(is.na(manual_classifications_df$marker_gene_classification))){
  has_marker_gene <- FALSE
  message("No annotations were available using only marker gene expression. 
          Any plots comparing CopyKAT to marker gene annotation will be skipped.")
} else {
  has_marker_gene <- TRUE 
}

### 2024-05-23 analyses/cell-type-ewings/template_notebooks/04-infercnv.Rmd

# check if marker gene annotations are present 
if(all(is.na(manual_classifications_df$marker_gene_classification))){
  has_marker_gene <- FALSE
} else {
  has_marker_gene <- TRUE 
}

>>>>

# check if marker gene annotations are present 
if(all(is.na(manual_classifications_df$marker_gene_classification))){
  has_marker_gene <- FALSE
  message("No annotations were available using only marker gene expression. 
          Any plots comparing InferCNV to marker gene annotation will be skipped.")
} else {
  has_marker_gene <- TRUE 
}
